\vspace{1.0cm} \Large \bf Integrating influenza antigenic dynamics with molecular evolution

### 2013-03-25 flux.tex
Include 100-word statement of significance for PNAS.

>>>>

%%% SIGNIFICANCE %%%
\section*{Significance}

Influenza viruses continually evolve in antigenic phenotype to escape human immunity.
In this study, we develop a new method to characterize influenza antigenic phenotype from immunological and genetic data.
We use this method to assess patterns of antigenic evolution in four different influenza viruses and show that antigenic drift strongly influences viral success.
Drifted viruses cause larger seasonal outbreaks and outcompete less evolved viruses.
A more thorough understanding of the predictors of viral success may allow selection of vaccine strains better matched to the population of influenza viruses circulating when the vaccine is deployed.
